A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2019-04-08 for_submission/rvaught_2018.tex
added Martin_2013_galaxy

The \added{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2} with \added{maximum outflow} velocities $\Delta v_{\rm max}$ $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA. \added{These maximum outflow velocities (listed in Table \ref{tab:prop}) are determined from fitting a two-velocity component model to the absorption line profiles. The two-component model assumes that there is an absorption component due to stellar atmospheres and the interstellar medium with a velocity fixed at systemic, as well as a ``flow'' absorption component with a velocity that is allowed to float.  %that both contribute to the overall line profile.
The maximum outflow velocity $\Delta v_{\rm max}$ is the fitted central velocity of the flow component, $v_{\rm flow}$, minus the fitted Doppler parameter, $b_{D,\rm flow}/\sqrt{2}$.  It thus is indicative of the most extreme flow velocities traced by each absorption line profile.
The two-component model does not explicitly include a contribution to the line profile from scattered emission, which
can be significant at velocities close to systemic \citep{Prochaska_2011}.  However, as discussed in \cite{Rubin_2014}, it is expected that scattered emission will primarily tend to reduce the strength of the fitted systemic component, and will have a minor effect on fitted flow component velocities and line widths (see their Appendix C).
%The use of the two-component model mitigates the effect of scattered emission
%on the fitted velocity.
%filling up the absorption line which in turn pushes the trough of the line blueward. It is assumed that the resonant emission will reduce the systemic %velocity, leaving the flow velocity to characterize the outflow. 
%The qualitative context of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}
}

@@

\begin{deluxetable*}{c c D D D c D}
\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
\tablehead{\colhead{Object\tablenotemark{a}} &  \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} &\colhead{$\Delta v_{\rm max}$\tablenotemark{b}} &\multicolumn2c{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$\tablenotemark{c}} \\ 
\colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(km s$^{-1}$)} & \multicolumn2c{(\AA)} & \multicolumn2c{}}
\decimals
\startdata
J033225.26-274524.0 (J.26)     &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   &   $-187_{-16}^{+12}$ & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
J033229.64-274242.6 (J.64)     &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &   $-378_{-12}^{+12}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
J033230.03-274347.3 (J.03)     &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   &   $-400_{-64}^{+132}$ & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
J033230.57-274518.2 (J.57)     &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ &   $-266_{-38}^{+44}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
J033231.36-274725.0 (J.36)     &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ &   $-168_{-126}^{+33}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
\enddata
%\tablenotetext{a}{\added{Galaxy names include their  are named according to the object R.A and DEC. position.}}
\tablenotetext{a}{\added{Galaxy names include their R.A. and Declination in the J2000.0 epoch.  The names in parentheses are used to identify each object throughout the paper.}}
\tablenotetext{b}{\added{Maximum outflow velocity traced by \ion{Mg}{2}, $\Delta v_{\rm max} \approx v_{\rm flow}- b_{D,\rm flow}/\sqrt{2}$, where $b_{D,\rm flow}$ is the fitted Doppler parameter and $v_{\rm flow}$ is the fitted central velocity of the ``flow'' component in a two-component model of the absorption line profile.}}
\tablenotetext{c}{\added{Total $V$-band optical depth of dust attenuating light from the young stellar population in each galaxy as modeled by MAGPHYS.  This includes contributions from dust in both \ion{H}{2}  regions and the ambient ISM.} }
\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
\end{deluxetable*}

@@

\section{Discussion}\label{sec:discussion}
\subsection{Previous Detections of Extended \ion{Mg}{2} Emission}
Previous constraints on the brightness of scattered \ion{Mg}{2} emission were reported by \cite{Rubin_2011}. In this work the authors studied emission from the starburst galaxy TKRS 4389 at $z = 0.69$ with a SFR of $49.8\msunperyr$. This emission was detected in a 2-dimensional Keck/LRIS spectrum, with flux from the emission reaching $(8.0 \pm 0.4)$ and $(4.4 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $(4.0 \pm 0.3)$ and $(2.5 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ in two independent locations spatially offset from the galaxy continuum. The flux from both emission lines can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 arcsec$^2$ aperture. Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs. SFR (left panel) and vs.\ $\log M_*/M_{\odot}$ (middle panel). These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.57]{figure11.pdf}%all_limitsv2.pdf
\caption{Comparison of our detection limits to the SB, measured in two independent locations spatially offset from the galaxy continuum, of extended \ion{Mg}{2} emission around the starburst galaxy TKRS 4389. These surface brightness constraints are plotted vs.\ SFR (left), stellar mass (middle), and specific SFR (right). Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$. The symbol colors indicate the same galaxies as in Figure \ref{fig:ew_comb}}
\label{fig:all_limits}
\end{figure*}

>>>>

The \textbf{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2} with \textbf{maximum outflow} velocities $\Delta v_{\rm max}$ $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA. \textbf{These maximum outflow velocities (listed in Table \ref{tab:prop}) are determined from fitting a two-velocity component model to the absorption line profiles. The two-component model assumes that there is an absorption component due to stellar atmospheres and the interstellar medium with a velocity fixed at systemic, as well as a ``flow'' absorption component with a velocity that is allowed to float.  %that both contribute to the overall line profile.
The maximum outflow velocity $\Delta v_{\rm max}$ is the fitted central velocity of the flow component, $v_{\rm flow}$, minus the fitted Doppler parameter, $b_{D,\rm flow}/\sqrt{2}$.  It thus is indicative of the most extreme flow velocities traced by each absorption line profile.
The two-component model does not explicitly include a contribution to the line profile from scattered emission, which
can be significant at velocities close to systemic \citep{Prochaska_2011}.  However, as discussed in \cite{Rubin_2014}, it is expected that scattered emission will primarily tend to reduce the strength of the fitted systemic component, and will have a minor effect on fitted flow component velocities and line widths (see their Appendix C).
%The use of the two-component model mitigates the effect of scattered emission
%on the fitted velocity.
%filling up the absorption line which in turn pushes the trough of the line blueward. It is assumed that the resonant emission will reduce the systemic %velocity, leaving the flow velocity to characterize the outflow. 
%The qualitative context of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}
}

@@

\begin{deluxetable*}{c c D D D c D}
\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
\tablehead{\colhead{Object\tablenotemark{a}} &  \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} &\colhead{$\Delta v_{\rm max}$\tablenotemark{b}} &\multicolumn2c{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$\tablenotemark{c}} \\ 
\colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(km s$^{-1}$)} & \multicolumn2c{(\AA)} & \multicolumn2c{}}
\decimals
\startdata
J033225.26-274524.0 (J.26)     &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   &   $-187_{-16}^{+12}$ & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
J033229.64-274242.6 (J.64)     &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &   $-378_{-12}^{+12}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
J033230.03-274347.3 (J.03)     &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   &   $-400_{-64}^{+132}$ & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
J033230.57-274518.2 (J.57)     &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ &   $-266_{-38}^{+44}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
J033231.36-274725.0 (J.36)     &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ &   $-168_{-126}^{+33}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
\enddata
%\tablenotetext{a}{\added{Galaxy names include their  are named according to the object R.A and DEC. position.}}
\tablenotetext{a}{\textbf{Galaxy names include their R.A. and Declination in the J2000.0 epoch.  The names in parentheses are used to identify each object throughout the paper.}}
\tablenotetext{b}{\textbf{Maximum outflow velocity traced by \ion{Mg}{2}, $\Delta v_{\rm max} \approx v_{\rm flow}- b_{D,\rm flow}/\sqrt{2}$, where $b_{D,\rm flow}$ is the fitted Doppler parameter and $v_{\rm flow}$ is the fitted central velocity of the ``flow'' component in a two-component model of the absorption line profile.}}
\tablenotetext{c}{\textbf{Total $V$-band optical depth of dust attenuating light from the young stellar population in each galaxy as modeled by MAGPHYS.  This includes contributions from dust in both \ion{H}{2}  regions and the ambient ISM.} }
\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
\end{deluxetable*}

@@

\section{Discussion}\label{sec:discussion}
\subsection{Previous Detections of Extended \ion{Mg}{2} Emission}
Previous constraints on the brightness of scattered \ion{Mg}{2} emission were reported by \cite{Rubin_2011} and \cite{Martin2013}. In \cite{Rubin_2011} the authors studied emission from the starburst galaxy TKRS 4389 at $z = 0.69$ with a SFR of $49.8\msunperyr$. This emission was detected in a 2-dimensional Keck/LRIS spectrum, with flux from the emission reaching $(8.0 \pm 0.4)$ and $(4.4 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $(4.0 \pm 0.3)$ and $(2.5 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ in two independent locations spatially offset from the galaxy continuum. The flux from both emission lines can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 arcsec$^2$ aperture.

\textbf{In addition to TKRS 4389, a second detection of extended \ion{Mg}{2} emission is reported in \cite{Martin2013}. In this study, the authors spatially resolve extended \ion{Mg}{2} emission in the galaxy, 32016857, at a redshift of $z=0.9392$ with SFR of $\sim 80\msunperyr$. Detected using a 2-dimensional Keck/LRIS spectrum, the \ion{Mg}{2} emission extends out to $\sim11$ kpc eastward away from the galaxy continuum. In the integrated spectrum, the observed flux in \ion{Mg}{2} emission is approximately $1.5$$\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $ 1.0$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ to 20\% accuracy. The extended \ion{Mg}{2} component contributes up to 46\% of the total integrated \ion{Mg}{2} flux. We convert the extended flux to SB using a 1 arcsec$^2$ aperture.
Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxies TKRS 4389 and 32016857 vs. SFR (left panel) and vs.\ $\log M_*/M_{\odot}$ (middle panel). These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.}

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.57]{figure11.pdf}%all_limitsv2.pdf
\caption{Comparison of our detection limits to the SB, measured in two independent locations spatially offset from the galaxy continuum, of extended \ion{Mg}{2} emission around the starburst galaxy TKRS 4389 \textbf{and one independent location spatially offset from the galaxy continuum eastward of 32016857}. These surface brightness constraints are plotted vs.\ SFR (left), stellar mass (middle), and specific SFR (right). Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$ and 32016857 with SFR $\sim 80 \msunperyr$. The symbol colors indicate the same galaxies as in Figure \ref{fig:ew_comb}}
\label{fig:all_limits}
\end{figure*}
